\documentclass[a4paper,12pt]{article}
\begin{document}
Yongzuan Wu

wu68

cs573

HW 5

Problem 4


reference: http://en.wikipedia.org/wiki/Maximum_flow_problem

(a)

Proof: Here is a counter example

For the input array $M[1..n,1..n]$, 

$$
M[i][j] = \left\{ \begin{array}{rl}
  1 &\mbox{ if ($i=1$ and $j\in [1..n-1]$)or($i=n$ and $j\in [2..n]$)} \\
  0 &\mbox{ otherwise}
       \end{array} \right.      
$$ 

The greedy algorithm find a good path $M[1,1]\rightarrow M[1,2] \rightarrow M[1,3] \rightarrow M[n,3] \rightarrow M[n,n]$, which covers $n$ marked cells. Yet the remaining configuration needs at least two more path to cover, since both $M[n,2]$ and $M[1,4]$ are uncovered.

(b)


We reduce the problem to a bipartite graph matching.

Given the array $M[1..n,1..n]$, first we find the set $V=\{v_{ij}\left| M[i,j]=1\}$. Then We construct a directed graph $G=(K,E)$, where 

$$
E=\{(u,w)\left| u=v_{ij}, w=v_{i'j'},  u\neq v, i'\geq i,  j'\geq j\}
$$

In $G$, a vertex represent a marked cell, and an edge $(u,w)$ represents a monotone path from cell $u$ to cell $w$. It's esay to see that the problem is equivalent to finding a collection of paths in $G$ that covers all vertices.

We can reduce this problem to bipartite graph matching.

Let $G'=(V\cup V',E')$ be a bipartite graph, where $V'=\{v'_{ij}\left| v_{ij}\in V\}$,  $E=\{(v_{ij},v'_{i'j'})\left| (v_{ij},v_{i'j'})\in E\}$. Let $M$ be a matching of G. Every edge in $M$ corresponds to an edge in $G$. Then a vertex $v'_{ij} \in V'$ that is not covered by $M$ indicates that $v_{ij}$ has no succedent in its path, i.e. it is the end point in its path. Thus the number of paths in the collection defined by $M$ is $n-\left|M\right|$. Therefore the smallest number of paths covering $G$ is given by ($n-$the maximum matching of G). Thus the algorithm follows,

\

UncoverCell($M[1..n,1..n]$)

\ construct $G'$ as described above

\ compute the maximum matching $M$ of $G'$

\ return  $n-\left|M\right|$

\

Analysis:
We could use the Ford-Fulkerson algorithm to compute the maximun matching. The algortihm runs in $O(VE)$. By construction, $\left|V\right|=O(n^{2})$, $\left|E\right|=O(n^{4})$, thus the running time is $O(n^{6})$

\end{document}